### 2023-04-26 paper.tex
one sentence per line

Typically, some regions in a chromosome will have very similar methylation status in all cells, while other regions show variability in methylation across cells.
For instance, it is known  since long that CpG-rich promoters of housekeeping genes are unmethylated, and that a large proportion of the remaining genome is highly methylated regardless of cell type \citep{bird1986cpg}.
In contrast, DNA methylation at certain genomic features such as enhancers is more dynamic (e.g., \citet{argelaguet2019gastru}), and thus more variable across cells.
Only the latter regions are of value for our goal of quantitating dissimilarity between cells.
We call these the variably methylated regions (VMRs). % maybe mention the parallel to highly variable genes in scRNAseq?

>>>>

Typically, some regions in a chromosome will have very similar methylation status in all cells, while other regions show variability in methylation across cells.
For instance, it is known  since long that CpG-rich promoters of housekeeping genes are unmethylated, and that a large proportion of the remaining genome is highly methylated regardless of cell type \citep{bird1986cpg}.
In contrast, DNA methylation at certain genomic features such as enhancers is more dynamic \citep[e.g.,][]{argelaguet2019gastru}, and thus more variable across cells.
Only the latter regions are of value for our goal of quantitating dissimilarity between cells.
We call these the variably methylated regions (VMRs). % maybe mention the parallel to highly variable genes in scRNAseq?
